Supporting Information: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-16 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
final draft ready for review

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{array}
\usepackage{multirow}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

\title{Supporting Information: Time Series Modeling of Varying Complexity Captures 
Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_URE.pdf}
  \caption{Urea}\label{fig:URE_msddm_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_ACH.pdf}
  \caption{Acetic Acid}\label{fig:ACH_msddm_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_msddm_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_MET.pdf}
  \caption{Methanol}\label{fig:MET_msddm_fpt_distributions}
  \end{subfigure}
  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
  first passage time distributions generated by 1000 realizations of the 
  Markov state dependent dynamical model. Note that we generated 10 times less
  realizations of the MSDDM which leads to noisier histograms. We show that
  this has a negligible effect on the fits in Figure~\ref{fig:flux_curve_sensitivity}.}\label{fig:msddm_fpt_fits}
  \end{figure}

@@

>>>>

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{array}
\usepackage{multirow}

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_URE.pdf}
%  \caption{Urea}\label{fig:URE_msddm_fpt_distributions}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_ACH.pdf}
%  \caption{Acetic Acid}\label{fig:ACH_msddm_fpt_distributions}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_GCL.pdf}
%  \caption{Ethylene Glycol}\label{fig:GCL_msddm_fpt_distributions}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_MET.pdf}
%  \caption{Methanol}\label{fig:MET_msddm_fpt_distributions}
%  \end{subfigure}
%  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
%  first passage time distributions generated by 1000 realizations of the 
%  Markov state dependent dynamical model. Note that we generated 10 times less
%  realizations of the MSDDM which leads to noisier histograms. We show that
%  this has a negligible effect on the fits in Figure~\ref{fig:flux_curve_sensitivity}.}\label{fig:msddm_fpt_fits}
%  \end{figure}

@@

%  \newpage
%  \section{Explanation of Under-Estimated MSDDM $\beta$ Values}\label{section:beta_estimates}
%  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
%  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
%  Turning first to the model itself, we have designed it to ensure that the magnitude of the
%  hops in the series of transitions between states are anti-correlated from start to finish. 
%  This assumes that the transition correlation structure is unaffected by the
%  sub-trajectories between each state transition. Each time a state transition occurs, one
%  must initialize a new time series sub-trajectory with its own correlation structure. 
%  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
%  %in each state is relatively short making the accuracy of the correlation structure 
%  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
%  %$\sigma$ in trapped states. 
%  Since we add the transitional hop lengths to each end of
%  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
%  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
%  MSDDM to completely immobilize particles except when they transition between states. 
%  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
%  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
%  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
%  To generate the curves in Figure~\ref{M-fig:flux_curves_msddm}, we needed to correlate 
%  25--1000 times more hops than for the MSD predictions in Figure~\ref{M-fig:msddm_performance}. 
%  In short, it is computationally infeasible to use enough terms to accurately incorporate
%  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
%  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
%  fractional Brownian motion, for which we have an exact simulation method, in place of 
%  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
%  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
%  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
%  of FLM.  
%  \begin{figure}[h]
%  \begin{subfigure}{0.43\textwidth}
%  \includegraphics[width=\textwidth]{beta_hurst.pdf}
%  \caption{}\label{fig:beta_hurst}
%  \begin{subfigure}{0.52\textwidth}
%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
%  \caption{}\label{fig:beta_parameters}
%  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
%  %MRS6: should try to lead with what the overall results/conclusions are.  What does it mean that parameters are larger or smaller?  What should the reader take from the discussion?  Should it be in supportinig?
%  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
%  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
%  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
%  sub-trajectories between state transitions decorrelate transitional hops and because
%  our FLM simulation procedure does not accurately correlate hops after long time lags. 
%  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
%  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
%  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
%  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
%  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
%  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
%  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
